---
title: "P8105_hw3_REN XIN"
output: github_document
date: "2022-10-12"
---
```{r}
library(tidyverse)
library(readxl)
library(readr)
library(dplyr)
library(p8105.datasets)
library(ggplot2)
```

```{r}
devtools::install_github("p8105/p8105.datasets",force = TRUE)
data("instacart")
```



Problem 2:

```{r}
Accel = 
  read_excel("accel_data.xlsx")
Accel_2 = Accel %>%
  mutate(weekday = case_when(
    day == "Monday" ~ "weekday",
    day == "Tuesday" ~ "weekday",
    day == "Wednesday" ~ "weekday",
    day == "Thursday" ~ "weekday",
    day == "Friday" ~ "weekday",
    day == "Saturday" ~ "weekend",
    day == "Sunday" ~ "weekend",
    TRUE  ~""
  ))
```


```{r}
Accel_2=
  mutate(
    Accel, sum=rowSums(Accel[4:1443], na.rm = TRUE)
  )
Accel_2=Accel_2 %>%
  pivot_longer(activity.1:activity.1440,names_to = "activity_nb", values_to = "count")

ggplot(Accel_2,aes(x=activity_nb, y=count , color = day ))+
  geom_point()
```

Description: 
The Accel_2 has  'nrow(Accel_2)' row and 'ncol(Accel_2)'  columns.The variables included week, day_id, day,sum, activity_nb, counnt. There are 'nrow(Accel_2)' observations in total. There are no apparent trend. 

Problem 3
```{r}
devtools::install_github("p8105/p8105.datasets", force = TRUE)
```
```{r}
library(p8105.datasets)
data("ny_noaa")
```
```{r}
nrow(ny_noaa)
ncol(ny_noaa)
```

Description: 
This dataset(ny_noaa) has 'nrow(ny_noaa)' row and 'ncol(ny_noaa)'  columns. There are total 7 row, which are id、date、prcp、snow、snwd 、tmax and tmin.Those are key Variables. Each row represent the weather of NY from '1981-01-01' to '2010-12-31'. There are also some data missing. Find out how much data is missing are 'table(is.na(ny_noaa$prcp))'、table(is.na(ny_noaa$snow))、table(is.na(ny_noaa$snwd))、table(is.na(ny_noaa$tmax))、table(is.na(ny_noaa$tmin)).


```{r}
ny_noaa_clearn = separate(ny_noaa,date, into= c("year","month",'day'),sep= "-")
ny_noaa_snow = as.data.frame(table(ny_noaa_clearn$snow))
```
Description: 
the most commonly observed values is O, which appear 2008508 times.The reason why 0 is the most commonly is the weather of snow and low temperature are unusual in one year.

Ny_noaa_Jan and July

```{r}
ny_noaa_clearn= ny_noaa_clearn %>% 
  mutate(
  month=as.double(month),
  year=as.double(year)
)
ny_noaa_filt=ny_noaa_clearn %>% 
  filter(month==1|month==7)
```
 
